---
title: "Homework 4"
author: "Yuxuan Chen"
date: "2/24/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Consider the Physicians Health Study, where subjects were randomized either to aspirin or placebo. Assume equal allocation.

Simple randomization. Using the seed 938134 in the SAS code on slide #33 (entitled ‘How to perform a simple randomization’) in the lecture 5 slide deck and starting with the first line in the output, determine the treatment allocation of the first eight recruited subjects (who have given consent and satisfied eligibility criteria). Mark X to specify the treatment group for each subject. 
Asp stands for ‘aspirin’; Pla stands for ‘placebo.’ 


```{r}
set.seed(938134)
randnum <- ceiling(runif(100, 0, 9))
randnum[randnum<=6]
```

```{r}
set.seed(3374)
randnum <- ceiling(runif(100, 0, 9))
randnum[randnum<=2]

set.seed(4875)
randnum <- ceiling(runif(100, 0, 9))
randnum[randnum<=2]

set.seed(1389)
randnum <- ceiling(runif(100, 0, 9))
randnum[randnum<=2]

set.seed(2973)
randnum <- ceiling(runif(100, 0, 9))
randnum[randnum<=2]
```


